---
title: "Example arguments for sqlDT"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example arguments for sqlDT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
library(sqlDT)
data_iris <- iris
names(data_iris) <- c("SepalLength", "SepalWidth", "PetalLength", "PetalWidth", "Species")
```

The `sqlDT` function has several options that can be used to customize the behavior and appearance of the resulting DataTable. Below are some examples of how to use these options.

# Query options using AlaSQL

You can use various SQL queries to manipulate the data before displaying it in the DataTable. The data.frame used for the query is denoted by a "?" in the query.

For a full list of supported SQL statements, see the Alasql GitHub page for [Supported SQL statements](https://github.com/AlaSQL/alasql/wiki/Supported-SQL-statements).

For a full list of supported SQL keywords, see the AlaSQL GitHub page for [SQL Compatability](https://github.com/alasql/alasql/wiki/SQL%20keywords).

Here are some example use cases with the `sqlDT` function:

## Select all data

```{r query-options}
sqlDT(data_iris, query = "SELECT * FROM ?")
```

## Select specific columns

```{r select-columns}
sqlDT(data_iris, query = "SELECT SepalLength, SepalWidth, Species FROM ?")
```

## Use aliases

```{r aliases}
sqlDT(data_iris, query = "SELECT SepalLength AS SL, SepalWidth AS `Sepal Width` FROM ?")
```

## Aggregate functions
```{r aggregate-functions}
sqlDT(data_iris, query = "SELECT Species, AVG(SepalLength) AS Avg_SepalLength FROM ? GROUP BY Species")
```

## Filtering data
```{r filtering-data}
sqlDT(data_iris, query = "SELECT * FROM ? WHERE SepalLength > 5.0")
```

## Sorting data
```{r sorting-data}
sqlDT(data_iris, query = "SELECT * FROM ? ORDER BY SepalLength DESC")
```

# DataTable options

The result of the query is returned using the DataTables javascript library. The `sqlDT` function also allows you to customise the DataTable using various options. 

For a full list of customisations available, see the DataTables documentation for [Options](https://datatables.net/reference/option/).

Here are some example use cases with the `sqlDT` function:

## Pagination
```{r pagination}
sqlDT(data_iris, query = "SELECT * FROM ?", options = list(pageLength = 5))
```

## Searching
```{r searching}
sqlDT(data_iris, query = "SELECT * FROM ?", options = list(searching = TRUE))
```

## Column visibility
```{r column-visibility}
sqlDT(data_iris, query = "SELECT * FROM ?", options = list(columnDefs = list(list(visible = FALSE, targets = c(2,3)))))
```

## Export buttons
```{r export-buttons}
sqlDT(data_iris, query = "SELECT * FROM ?", options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

## Scrolling
```{r scrolling}
sqlDT(data_iris, query = "SELECT * FROM ?", options = list(scrollY = '200px', scrollCollapse = TRUE, paging = FALSE))
```

## Sorting
```{r sorting}
sqlDT(data_iris, query = "SELECT * FROM ?", options = list(order = list(list(0, 'desc'))))
```
